Comparing R packages for calculation of persistent homology

### 2020-03-08 tdabench-paper/tdabench.Rmd
caption edits

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig1.png}
  \caption{
    \textbf{Calculating persistent homology of a torus with three TDA libraries.}
    Average runtime (mean $\pm$ SD, $n=10$) for each TDA library (denoted by color) is plotted against point cloud size.
    Homological features up to 2 dimensions were calculated.
    Time complexity follows a power law for all three libraries (see GitHub repo for regression details).
    Although the libraries have similar runtimes for smaller point clouds, Dionysus has a clear disadvantage when the number of points exceeds 100.
    When the number of points exceeds 200, Ripser has a clear advantage over GUDHI, which maintains its advantage over Dionysus.
  }
\label{fig:tor}
\end{figure}

@@

\begin{widefigure}
  \centering
  \includegraphics[height=2in]{../Figures/Final_Figures/fig2.png}
  \caption{
    \textbf{Calculating persistent homology of round point clouds of varying dimensions with three TDA libraries.}
    Average runtime (mean $\pm$ SD, $n=10$) for each TDA library (denoted by color) is plotted against point cloud size and faceted by data dimension.
    Left panel compares library performance for a 2-dimensional circular point cloud; center panel for a 3-dimensional spherical point cloud; and right panel for a 4-dimensional hyperspherical point cloud.
    Maximum feature dimensions (one less than data dimension) were calculated in each case.
  }
\label{fig:cir}
\end{widefigure}

>>>>

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig1.png}
  \caption{
    \textbf{Calculating persistent homology of a torus with three TDA libraries.}
    Average runtime (mean $\pm$ SD, $n=10$ iterations per data point) for each TDA library (denoted by color) is plotted against point cloud size.
    Homological features up to 2 dimensions were calculated.
    Time complexity follows a power law for all three libraries (see GitHub repo for regression details).
    Although the libraries have similar runtimes for smaller point clouds, Dionysus has a clear disadvantage when the number of points exceeds 100.
    When the number of points exceeds 200, Ripser has a clear advantage over GUDHI, which maintains its advantage over Dionysus.
  }
\label{fig:tor}
\end{figure}

@@

\begin{widefigure}
  \centering
  \includegraphics[height=2in]{../Figures/Final_Figures/fig2.png}
  \caption{
    \textbf{Calculating persistent homology of round point clouds of varying dimensions with three TDA libraries.}
    Average runtime (mean $\pm$ SD, $n=10$ iterations per data point) for each TDA library (denoted by color) is plotted against point cloud size and faceted by data dimension.
    Left panel compares library performance for a 2-dimensional circular point cloud; center panel for a 3-dimensional spherical point cloud; and right panel for a 4-dimensional hyperspherical point cloud.
    Maximum feature dimensions (one less than data dimension) were calculated in each case.
  }
\label{fig:cir}
\end{widefigure}
